---
title: "p8105_hw1_yl4604"
author: Yu Liu 
output: github_document
---

This is my solution to HW1

```{r}
library(tidyverse)
library(ggplot2)

```

## Problem 1

Create a data frame with specified elements

```{r dataframe}

prob1_df = tibble(
  samp = rnorm(10),
  samp_gt_0 = samp > 0,
  char_vec = c('a', 'b', 'c', 'd', 'e', 'f', 'g', 'h', 'i', 'j'),
  factor_vec = factor(c('low', 'high', 'low', 'median', 'low', 'low', 'high', 'high', 'low', 'high'))
)

```

Take the element mean of each variables in my dataframe
```{r mean, eval = FALSE}
mean(pull(prob1_df, samp))
mean(as.numeric(pull(prob1_df, samp_gt_0)))
mean(as.numeric(pull(prob1_df, char_gt_0)))
mean(as.numeriC(pull(prob1_df, factor_vec)))
```
I can take  means of numeric and logical but not character or factor

```{r multiply}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)

```

##problem 2 

```{r penguins}
data('penguins', package = 'palmerpenguins')
summary(penguins)
```
The variable names in the dataset 'penguins' are: ' `r names(penguins)` '.    
There are `r unique(pull(penguins, species))`  species in the dataset, on `r unique(pull(penguins, island))` island.
There are total
The range of penguins bill length is (`r range(pull(penguins, bill_length_mm), na.rm = TRUE)` )mm, minimum length is `r min(pull(penguins, bill_length_mm), na.rm = TRUE)`mm, maximum length is `r max(pull(penguins, bill_length_mm), na.rm = TRUE)`mm, average length is `r mean(pull(penguins, bill_length_mm), na.rm = TRUE)`mm.  
The range of bill depth is (`r range(pull(penguins, bill_depth_mm), na.rm = TRUE)`) mm, minimum depth is `r min(pull(penguins, bill_depth_mm), na.rm = TRUE)`mm, maximum depth is `r max(pull(penguins, bill_depth_mm), na.rm = TRUE)`mm, average depth is `r mean(pull(penguins, bill_depth_mm), na.rm = TRUE)`mm.  
The range of flipper length is ( `r range(pull(penguins, flipper_length_mm), na.rm = TRUE)`) mm, minimum length is `r min(pull(penguins, flipper_length_mm), na.rm = TRUE)`mm, maximum length is `r max(pull(penguins, flipper_length_mm), na.rm = TRUE)`mm, average length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`mm.  
The range of body mass is (`r range(pull(penguins, body_mass_g), na.rm = TRUE)` )g. minimum mass is `r min(pull(penguins, body_mass_g), na.rm = TRUE)`mm, maximum mas is `r max(pull(penguins, body_mass_g), na.rm = TRUE)`mm, average mass is `r mean(pull(penguins, body_mass_g), na.rm = TRUE)`mm.  

The total female is `#

The size of the dataset penguins is `r nrow(penguins)` * `r ncol(penguins)` .

The mean filpper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`mm.

```{r scatterplot}
ggplot(penguins, 
       aes(x = bill_length_mm, 
           y = flipper_length_mm, 
           colour = species) )+ geom_point()
ggsave

```


